A Pandemic-Scale Ancestral Recombination Graph for SARS-CoV-2

### 2025-10-22 latex/main.tex
Add section on evaluation via sims

[Section laying out why we don't use simulation.]
Benchmarking
against extensive empirical results for SARS-CoV-2 rather than simulations
leverages a uniquely rich literature and dataset, ensuring that the resulting
ARG reflects both biological realism and computational reproducibility.

>>>>

% NOTES: This section is a bit weird as it's like a discussion point, but is 
% too technical and negative to go in there. Nonetheless, we do need to address
% this point somewhere, as it'll be something that would surely come up.
% We might get asked to do some simulations, but let's try and steer the 
% reviewer into asking us to do something simple like crudely recombining
% different lineages and seeing what we get.

[NOTE: first draft]
Sc2ts is a new method to infer ARGs for SARS-CoV-2, and the standard practise 
is to evaluate new inference methods via a simulation analysis.  
We have, instead, focused our validation efforts on comparing the output 
produced by sc2ts to known results.
Benchmarking against these extensive empirical results rather 
than simulations leverages the uniquely rich literature, 
ensuring that the resulting ARG (the primary contribution of this work)
reflects biological reality.
While specialised simulation packages for SARS-CoV-2 data
% JK: did a search for VGSim, no recombination API included.
exist~\cite{Shchur2022vgsim,DeMaio2022phastsim} there is 
no support for recombination.
While bespoke simulation models can be created by manually recombining 
sequences in order to find false-positive and false-negative
rates, it is unclear how well this models the complexities 
of real data. Further work is needed to clarify the processes 
and frequency of recombination in SARS-CoV-2 in order to 
create simulations models that would inform this.
